Paper TITLE

### 2016-08-04 code/Paper.Rmd
changed more of Sri's stuff

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "year", y = "Median Adjusted Income (per persons)", 
       title = "APLmed by region")

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() + 
  scale_fill_manual(name = "Region", labels = regionNames)
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "ABLmed by region")

@@

It is interesting to note that the disparity between the incomes increases between the Northeast and WEstern regions and the Midwest and South. This is liekly because those living in the Midwest and South ten dto live in larger homes, housing more bedrooms on average, relative to their incomes due to the higher housing affordability. However, this should mean that their incomes go 'further,' as they have more purchasing parity given the lower cost of living compared to the Northeast and the West. This is not shown in the graphs, which indicate that the income levels are significantly different. However, if housing affordability was factored into the calcualtion, the income disparity would be far less if not almost nonexistent.

>>>>

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor the Number of People by Region") + 
  scale_color_discrete(name = "Region", labels = regionNames)

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor Number of Bedrooms by region") + 
  scale_color_discrete(name = "Region", labels = regionNames)

@@

It is interesting to note that the disparity between the incomes increases between the Northeast/Western regions and the Midwest/Southern Regions. This is liekly because those living in the Midwest and South ten dto live in larger homes, housing more bedrooms on average, relative to their incomes due to the higher housing affordability. However, this should mean that their incomes go 'further,' as they have more purchasing parity given the lower cost of living compared to the Northeast and the West. This is not shown in the graphs, which indicate that the income levels are significantly different. However, if housing affordability was factored into the calcualtion, the income disparity would be far less if not almost nonexistent.
